Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-01-06 paper.tex
update paper style, results, image assets

% Created 2023-01-04 Wed 14:12
% Intended LaTeX compiler: pdflatex
\documentclass[runningheads]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{amsmath, amsthm, amsfonts, enumerate}
\author{Alexander Groleau, Samay Maini, Jonathan Boarman}
\date{\today}
\title{Augraphy: An Augmentation Pipeline API for Modern Document Images}
\hypersetup{
 pdfauthor={Alexander Groleau, Samay Maini, Jonathan Boarman},
 pdftitle={Augraphy: An Augmentation Pipeline API for Modern Document Images},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.5.5)}, 
 pdflang={English}}
\begin{document}

@@

\section{Abstract}
\label{sec:orgb8a4f58}
We introduce Augraphy, a library for constructing feature augmentation pipelines for building modern document image datasets suitable for machine learning tasks. A discussion of prior art in the synthetic document image distortion space precedes description of the motivation for and structure of Augraphy. The library is used to produce a derivative of the NoisyOffice dataset, with which a simple convolutional neural network is trained and evaluated; the results of this experiment are discussed, followed by a look forward to further anticipated work.

\section{Introduction and Motivation}
\label{sec:org1b677d2}
Augraphy was created as a way to generate features that mimic those of real-world dirty documents, enabling users to produce datasets useful for training denoisers, layout classifiers, optical character recognizers, shadow and watermark removers, binarizers, deblurrers, defaders, layout classifiers, document image segmenters, and many other model types.\\

Training supervised learning models requires labeled datasets, which contain pairs of training data objects and associated labels, or ground-truths. However, collecting or otherwise determining a set of labels for training data is quite challenging.  In the case of text documents, most real-world dirty documents \emph{can't} come with clean ground-truths.\\

@@

\section{NoisyOffice}
\label{sec:orga476358}
Few datasets exist for out-of-the-box use in training document-specific models. Many other datasets containing modern documents exist, but are designed for tasks like layout detection [RDCL2019 cit], content extraction [Tobacco 800 cit], or handwriting recognition [ICDAR2019-CROHME-TDF cit]. In our investigations, the only publically available dataset we could find that was exclusively focused on digitally-generated documents was the NoisyOffice set [CASTRO-BLEDA].\\

The NoisyOffice dataset [paper link] was created as for document manipulation and analysis model training and validation. NoisyOffice includes three types of image:
\begin{enumerate}
\item ground truth images, created by printing some text and re-digitizing the physical document with a digital scanner,
\item synthetic noisy images, created by digitally fusing the text foreground with a background image of a coffee-stained or boot-printed page, using technique 1 above, and
\item real noisy images, created by physically stepping with boots onto physical documents, adding real coffee stains, and so on.
\end{enumerate}

While assembling the NoisyOffice database was a great service in its own right — no other such set seems to have been published — the NoisyOffice set is very limited:\\

\begin{itemize}
\item it contains only 3 font sizes (footnote, normal, large), 3 font types (typewriter, sans-serif, Roman), italicized and nonitalicized text, and 4 types of noise (folds, wrinkles, coffee stains, and footprints), for a total of 72 unique images.
\item the text is all English-language
\item the corpus has already been converted to grayscale, removing any choice about which desaturation algorithm to use
\item the image sizes provided are quite small (540x420), though double resolution images are also provided for use in training superresolution models
\end{itemize}

Rather than providing a direct answer to these, Augraphy does not (yet) generate the initial document image input to a pipeline, instead taking the approach of providing the tools for building a suitable dataset for any document image analysis taskwhile relying on users to supply the ground truth images.

\section{DocCreator}
\label{sec:orgf17073e}
In our investigations, the NoisyOffice database was the only preexisting dataset of images of modern documents with realistic distortions we could find; the situation is no better for document-specific feature augmentation tools, with only DocCreator seeming to occupy that niche.\\

@@

While an interesting piece of software in its own right, DocCreator is geared towards historical documents like ancient manuscripts and scrolls, and so is unfortunately poorly-suited to generating realistic images of \emph{modern} documents. Worse, the software is a monolithic what-you-see-is-what-you-get editor, with all internals written in C++, making it unsuitable for use either in a data augmentation pipeline or by the majority of researchers and industry practitioners who are much more familiar with Python-based tools and expect language-level integration. More frustrating still, the software is buggy and crashes often, making even successfully generating a single augmented document image quite an ordeal.\\

Augraphy was not designed with historical documents in mind, but neither did its design preclude that possibility. Instead, the focus is on modern documents generated at least in part digitally.

\section{Document Distortion, Theory \& Technique}
\label{sec:org24682f8}
Many approaches exist for adding features to an image, and many types of feature can be generated. The most common types of features added are Gaussian noise, blurring, geometric transformations like scaling, rotating, translating, and cropping, downsampling, font weighting, and so on.\\

@@

Some techniques exist for introducing these features into images of documents, including but not limited to the following:\\
\begin{enumerate}
\item Text can be generated independently of the paper texture, and can be overlaid onto the "paper" by a number of blending functions, allowing a variety of paper textures to be used. The NoisyOffice team did this.
\item Similarly, any markup features may be generated and overlaid by the same methods.
\item Documents can be digitized with a commercial scanner, or converted to a continuous analog signal and back with a fax machine.
\item The finished document image can be used as a texture and attached to a 3D mesh, then projected back to 2 dimensions to simulate physical deformation. DocCreator has a function to do this.
\end{enumerate}

@@

\section{Augraphy}
\label{sec:org4a1c65c}
We were unable to find any tools for producing training images of modern documents, in a way suitable for automated use. The Augraphy library is our attempt at filling this gap.\\

@@

Augraphy attempts to decompose the lifetime of features accumulating in a document by separating the pipeline into three phases: ink, paper, and post. The ink phase exists to sequence effects which specifically alter the printed ink — like bleedthrough from too much ink on page, extraneous lines or regions from a mechanically faulty printer, or fading over time — and transform them prior to "printing". The paper phase is concerned with transformations of the underlying paper on which the ink gets printed; here we find the PaperFactory generator for creating a random texture from a set of given texture images, as well as effects like random noise, shadowing, watermarking, and staining. After the ink and paper textures are computed separately, they are merged in the manner of Technique 1 from the previous section, simulating the printing of the document. After "printing", the document enters the post-phase, wherein it may undergo alterations that would affect an already-printed document out in the world. Augmentations are available here which simulate the printed page being folded along multiple axes, marked by handwriting or highlighter, faxed, photocopied, scanned, photographed, burned, stained, and so on. A brief description of each augmentation appears in a table in the next section.

\section{The Augraphy API}
\label{sec:orgd64a7b1}
The library was developed in Python, to allow maximal accessibility for practitioners, and was designed with an object-oriented structure, with concerns divided across a class hierarchy. When composed, different parts of the library interact to produce complex sequences of document image transformations, generating new synthetically-augmented datasets.\\

Modern frameworks for machine learning like \texttt{fastai} [Fastai: A Layered API for Deep Learning cit] aim to simplify the data handling requirements, and concordantly, the Augraphy development team takes great pains to ensure our library's ease-of-use and compatibility. We wanted the library to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so great care was taken to establish good defaults. The default Augraphy pipeline makes use of all of the augmentations available in Augraphy, with starting parameters selected after manual visual inspection of several thousand images. Adding a diverse array of realistic features to documents can be done with the following five-line incantation:

\begin{verbatim}
from augraphy import *
pipeline = default_augraphy_pipeline()
img = cv2.imread("image.png")
data = pipeline.augment(img)
augmented_img = data["output"]
\end{verbatim}

\subsection{Base}
\label{sec:org1182db0}
\texttt{augraphy.base} is the core of the library, containing the central class for augmentations, another class for sequences of augmentations, and the pipeline class itself. The base classes exist to coordinate the compilation of discrete transformations into a larger pipeline, and to facilitate the operation and maintenance of these.\\

There are four "main sequence" classes in \texttt{augraphy.base}, which together provide the bulk of the library's functionality. Two additional classes, \texttt{OneOf} and \texttt{PaperFactory}, provide additional variation to pipelines in ways explored soon.

\subsubsection{Augmentation}
\label{sec:org73d5fe0}
Augmentation is the most basic class in the project, and essentially exists as a thin wrapper over a probability value in the interval [0,1]. Every augmentation object is constructed with a probability of that augmentation being applied during the execution of a pipeline containing it.\\

@@

\subsubsection{AugmentationResult}
\label{sec:org6aeadfa}
After an augmentation is applied, the output of its execution is stored in an AugmentationResult object and passed forward through the pipeline. These objects also record an exact copy of the augmentation object that was instantiated and applied, as well as any metadata that might be relevant for debugging or other advanced use.

\subsubsection{AugmentationSequence}
\label{sec:org0192f11}
A list of Augmentations -- together with the intent to apply those Augmentations in sequence -- determines an AugmentationSequence, which is itself both an Augmentation and callable. In practice, these are the model for the pipeline phases discussed previously; they are essentially lists of Augmentation constructor calls which produce callable Augmentation objects of the various flavors explored in \hyperref[sec:orgea493da]{Augmentations}. AugmentationSequences are applied to the image during each of the \hyperref[sec:org6690404]{AugmentationPipeline} phases, and in each case yield the image, transformed by some of the Augmentations in the sequence.

\subsubsection{AugmentationPipeline}
\label{sec:org6690404}
The bulk of the innovation in Augraphy resides in the Augmentation pipeline, which is an abstraction over one or more events in a physical document's life. Events in this case could be the initial printing of the document when ink adhered to the paper material, or several weeks later when the document was adhered to a public board, annotated, defaced, and torn away from its securing staples. Fifty years later, our protagonist page resurfaces in the library archive during routine preservation-scanning efforts. Conservationists use delicate tools to gently position and record an image of the document, storing this in a public repository. An \texttt{AugmentationPipeline} can model this entire sequence of events, or any individual event within.\\

@@

The value added by the AugrapyPipeline class over a bare list of functions mapped over an image is principally in the collection of metadata: the output of an AugraphyPipeline application is a Python dictionary which contains not only the final image, but copies of every intermediate image, as well as information about the object constructors and their parameters that were used for each augmentation. This allows for easy inspection and fine-tuning of the pipeline definition to achieve outputs with desired features.

\subsubsection{OneOf}
\label{sec:orgb9ecb78}
Real-world processes generally allow for objects to exist in multiple states over time. To model the possibility that a document image has undergone one and only one of a collection of Augmentations, we use OneOf, which simply selects one of those Augmentations from a given list, and uses this to modify the image.

\subsubsection{PaperFactory}
\label{sec:org16fabe6}
We often print on multiple sizes and kinds of paper, and out in the world we certainly \emph{encounter} such diverse documents. We introduce this variation into the \texttt{AugmentationPipeline} by including \texttt{PaperFactory} in the \texttt{paper} phase of the pipeline. This augmentation checks a local directory for images of paper to crop, scale, and use as a background for the document image. The pipeline contains edge detection logic for lifting only text and other foreground objects from a clean image, greatly simplifying the "printing" onto another "sheet", and capturing in a reproducible way the construction method used to generate the NoisyOffice database. Taken together, \texttt{PaperFactory} makes it effectively possible to re-print a document onto other surfaces, like hemp paper, cardboard, or wood.

\subsection{Augmentations}
\label{sec:orgea493da}
The \texttt{base} modules provide scaffolding for working with general transformations on document images, called \texttt{augmentations}. We have already included many such transforms in the standard library, and have also provided \hyperref[sec:org8b47a22]{tools} for easily building new augmentations and integrating them into the Augraphy workflow.\\

@@

Table 1 contains a list of augmentations and a description of their simulated effects.

\begin{center}
\begin{tabular}{ll}
Augmentation & Effect\\
\hline
BadPhotoCopy & Regions of noise and shadow like those produced by a dirty photocopier.\\
BindingsAndFasteners & Staples, paper clips, punched holes, and other results of physical tools applied to a document.\\
BleedThrough & Ink bleeding through the page from the reverse side.\\
BookBinding & The page curling away from the scanner bed, towards the binding of a book or magazine.\\
Brightness & Adjusts the brightness of the whole image by a chosen multiplier.\\
BrightnessTexturize & Random noise in the brightnes channel of the image, which emulates various paper textures.\\
DirtyDrum & Deposits of dirt and ink-grime from dirty printer drums.\\
DirtyRollers & Dirty document scanners can leave roller lines on the page.\\
Dithering & Ordered or Floyd-Steinberg dithering is applied to simulate downsampling during document processing.\\
DustyInk & Random noise in the ink emulates dusty or inconsistent ink tone when combined with a blur.\\
Faxify & Faxing documents introduces artifacts related to errors in transmission.\\
Folding & Folded paper exhibits a visible warp effect around the folding axis\\
Gamma & Gamma controls several features, particularly relative brightness and contrast\\
Geometric & Basic spatial transformations like resizing, flipping, and rotation\\
Inkbleed & Creates a fuzzy edge emulating over-application of ink during printing.\\
Jpeg & JPEG compression artifacts (deep fry your documents!)\\
Letterpress & Regions of ink pressed unevenly onto paper by a printing press\\
LightingGradient & Introduces a shading pattern over the document, like a photograph with a partially-occluded light source\\
LowInkBlobs & When a printer's ink supply is low, some areas of prints receive less ink in spots than they should.\\
LowInkPeriodicLines & A set of parallel lines that repeat in a periodic fashion throughout the image.\\
LowInkRandomLines & A set of parallel lines randomly distributed throughout the image.\\
Markup & Adds strikethrough, highlighting, or underline effects to the text.\\
NoiseTexturize & Another method of emulating different paper textures, by introducing Gaussian noise into the paper layer.\\
PageBorder & Simulates the edges of background pages on one side of the foreground page.\\
PencilScribbles & Random pencil marks, like the product of an idle student.\\
SubtleNoise & Using a document scanner to digitize a page introduces imperfections in solid regions due to subtle lighting differences.\\
\end{tabular}
\end{center}

\subsection{Utilities}
\label{sec:org8b47a22}
Interoperability and flexibility are core requirements of any data augmentation library, so Augraphy includes several utility classes designed to improve developer experience during use in unforseen contexts, such as with other libraries.

\begin{center}
\begin{tabular}{ll}
Class & Purpose\\
\hline
ComposePipelines & Provides a means of composing two pipelines into one, allowing for the construction of complex pipeline algebras.\\
FigshareDownloader & Functions to query and download files from Figshare, a popular online repository of research data.\\
Foreign & Provides a means of wrapping augmentations from other projects, like Albumentations and imgaug.\\
Function & Wraps an arbitrary Python function or a list of such functions into an augmentation.\\
ImageOverlay & Places a given foreground image onto a given background, either randomly or at a specified location.\\
NoiseGenerator & Generates noise masks for placement on other images or in implementations of other augmentations.\\
OverlayBuilder & Creates an image mask containing other images, like hole punches or binder clips, for overlay onto a document.\\
\end{tabular}
\end{center}

\section{Deep Learning with Augraphy}
\label{sec:org4d4729d}
Augraphy aims to facilitate rapid dataset creation, advancing the state of the art for document image analysis tasks. This section describes a brief experiment using Augraphy to augment the NoisyOffice set, producing a corpus that is used to train a denoising convolutional neural network which outperforms an identically-structured model trained on only the provided NoisyOffice data. The NoisyOffice team set a baseline for others to follow in ["The NoisyOffice Database: A corpus to train supervised machine learning filters for image processing" CASTRO-BLEDA]. We continue to return to this database when testing our model training pipelines and new architectures, and felt it an appropriate set for Augraphy analysis.\\

Models were trained on an NVidia A100 GPU on Google Colaboratory. All preprocessing, training, and testing was done from a Jupyter notebook, published on GitHub.

\subsection{Model Architecture}
\label{sec:org83264cc}
To evaluate Augraphy, we trained a U-net convolutional neural network, built with the Keras library. This network achieved a high score on the NoisyOffice Kaggle competition [citation for Michal Brezák's notebook on Kaggle \url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}]; we selected this one for its simplicity and the clarity of its exposition, and use it with few changes. For more exploration of models trained to solve this competition's challenge, see Colin Priest's work here: [citation for Colin Priest \url{https://colinpriest.com/2015/11/15/an-even-dozen-denoising-dirty-documents-part-12/}].\\

This low-layer model contains two layers of a convolution, each followed by a ReLU activation function, then a batch normalization layer as the encoding step. After the encoding step, max pooling is applied, followed by dropout, to improve translation invariance of feature encoding and to avoid overfitting respectively. The decoding step closely mirrors the encoding step, and contains two layers of ReLU-activated convolutions followed by a batch normalization layer, but with the convolution dimensions reversed; in this case the model is "unpacking" higher-dimensional features from its low-dimensional latent representation. After the decoding step, we perform 2-dimensional upsampling, compensating for the 2D max pooling applied earlier. Finally, the output of previous layers is convolved with a 3x3 kernel, while retaining the same image dimensions. This final convolution uses the sigmoid function as its activation function. All convolution steps use a 3x3 kernel and pad edges with zeroes, the max pooling and upsampling steps both use 2x2 kernels, and a 50\% unit dropout rate was used.

\subsection{Data Generation}
\label{sec:orgd8c063f}
Despite recent techniques [Training Vision Transformers with Only 2040 Images, Vision Transformer for Small-Size Datasets, Training a Vision Transformer from scratch in less than 24 hours with 1 GPU] for reducing the volume of input data required to train models, data remains king; feeding a model more data during training can help ensure better latent representations of more features, improving robustness of the model and increasing its ability to generalize.\\

@@

\begin{verbatim}
ink_phase = []
paper_phase = []
post_phase = [BadPhotoCopy(), Markup()]

AugraphyPipeline(ink_phase, paper_phase, post_phase)
\end{verbatim}

Generating these 1440 images took 35 seconds with the rendering job spread across the 64 cores of an AWS c7g.16xlarge instance.

\subsection{Training Regime}
\label{sec:org4144ef4}
We fit the model architecture described in the previous section to both the NoisyOffice corpus and a derivative work generated with Augraphy applied to the NoisyOffice ground truth images.\\

@@

Both models were trained with mean squared error as the loss function, using the Adam optimizer.\\

The NoisyOffice model finished training with an average loss of 0.0010, a mean average error of 0.0150, validation loss of 7.4609e-04, validation mean average error of 0.0122. Training took an average of 190ms/step and 1s/epoch.\\

The Augraphy model finished training with an average loss of 0.0014, a mean average error of 0.0142, validation loss of 8.9985e-04, and validation mean average error of 0.0112. Training took roughly 218ms/step and 11s/epoch.

\subsection{Results}
\label{sec:org9fa72d2}
Sample predictions from each model on the validation task are presented in Figure 1. As expected, the NoisyOffice model performs admirably, but does struggle to fully remove the coffee stain feature, leaving some residue. The Augraphy model clearly outperforms the NoisyOffice model at stain removal, but does not generalize well to the folding and wrinkling noise; this was expected, since the Augraphy training data did not include fold or wrinkle features. Further, the Augraphy model overcompensates for the \texttt{BadPhotoCopy} behavior on text, by increasing the line thickness in the predicted text, resulting in a bold font.\\

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./images/sidebyside.png}
\caption{\label{fig:org74839c0}Comparison of the validation image (left) and the images predicted by the NoisyOffice model (center) and Augraphy model (right)}
\end{figure}

To compare the models' performance on the validation task, we considered the following metrics:
\begin{itemize}
\item Root mean square error (RMSE)
\item Structural similarity index (SSIM)
\item Peak signal-to-noise ratio (PSNR)
\end{itemize}

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {blue}
}
\usepackage{listings}
\usepackage{courier}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
\renewcommand{\floatpagefraction}{.8}%
\begin{document}

\title{Augraphy: An Augmentation Pipeline API for Modern Document Images}
\author{Alexander Groleau\inst{1,2} \and
Kok Wei Chee\inst{1} \and
Samay Maini\inst{1} \and
Jonathan Boarman\inst{1}}

\authorrunning{A. Groleau et al.}

\institute{Sparkfish LLC (\email{augraphy@sparkfish.com})
\and
Left Associates LLC (\email{research@left.associates})}

@@

\begin{abstract}
We introduce Augraphy, a library for constructing feature augmentation pipelines for building modern document image datasets suitable for machine learning tasks. A discussion of prior art in the synthetic document image distortion space precedes description of the motivation for and structure of Augraphy. The library is used to produce a derivative of the NoisyOffice dataset, with which a simple convolutional neural network is trained and evaluated; the results of this experiment are discussed, followed by a look forward to further anticipated work.
\end{abstract}

\section{Introduction and Motivation}
Augraphy was created as a way to generate features that mimic those of real-world dirty documents, enabling users to produce datasets useful for training denoisers, layout classifiers, optical character recognizers, shadow and watermark removers, binarizers, deblurrers, defaders, layout classifiers, document image segmenters, and many other model types.\\

Training supervised learning models requires labeled datasets, which contain pairs of training data objects and associated labels, or ground-truths. However, collecting or otherwise determining a set of labels for training data is quite challenging.  In the case of text documents, most real-world dirty documents /can't/ come with clean ground-truths.\\

@@

\section{NoisyOffice}
Many document-focused datasets exist, but most are designed for tasks like layout detection \cite{ref_RDCL2019}, content extraction \cite{ref_tobacco800}, or handwriting recognition \cite{ref_icdar}. the only publically-available dataset we could find that was exclusively focused on digitally-generated modern documents was NoisyOffice \cite{ref_NoisyOffice}.\\

This database \cite{ref_NoisyOfficeDatabase}, hosted on the UCI Machine Learning Repository \cite{ref_UCIMLR}, was created for training image processing filters, including denoisers and superresolution models. NoisyOffice includes three types of image:

\begin{enumerate}
\item ground truth images, created by printing some text and re-digitizing the physical document with a digital scanner,
\item synthetic noisy images, created by digitally fusing the text foreground with a background image of a coffee-stained or boot-printed page, using technique 1 above, and
\item real noisy images, created by physically stepping with boots onto physical documents, adding real coffee stains, and so on.
\end{enumerate}

Assembling the NoisyOffice database was a great service to the document analysis community, but for our purposes, the set is too limited:

\begin{itemize}
\item it contains only 3 font sizes (footnote, normal, large), 3 font types (typewriter, sans-serif, Roman), italicized and nonitalicized text, and 4 types of noise (folds, wrinkles, coffee stains, and footprints), for a total of 72 unique images.
\item the text is all English-language
\item the corpus has already been converted to grayscale, removing any choice about which desaturation algorithm to use
\item the image sizes provided are quite small (540x420), though double resolution images are also provided for use in training superresolution models.
\end{itemize}

Rather than providing a direct answer to these, Augraphy does not generate the initial document image input to a pipeline, instead taking the approach of providing the tools for building a suitable dataset for any document image analysis task while relying on users to supply the ground truth images.

\section{DocCreator}
In our investigations, the NoisyOffice database was the only preexisting dataset of images of modern documents with realistic distortions we could find; the situation is no better for document-specific feature augmentation tools, with only DocCreator \cite{ref_DocCreator} seeming to occupy that niche.\\

@@

While an interesting piece of software in its own right, DocCreator is geared towards historical documents like ancient manuscripts and scrolls, and so is unfortunately poorly-suited to generating realistic images of \textit{modern} documents. Worse, the software is a monolithic what-you-see-is-what-you-get editor, with all internals written in \texttt{C++}, making it unsuitable for use either in a semi-automated data augmentation pipeline or by the majority of researchers and industry practitioners who are much more familiar with Python-based tools and expect language-level integration.

\section{Document Distortion, Theory \& Technique}
Many approaches exist for adding features to an image, and many types of feature can be generated. The most common types of features added are Gaussian noise, blurring, geometric transformations like scaling, rotating, translating, and cropping, downsampling, font weighting, and so on.\\

@@

Some techniques exist for introducing these features into images of documents, including but not limited to the following:
\begin{enumerate}
\item Text can be generated independently of the paper texture, and can be overlaid onto the "paper" by a number of blending functions, allowing a variety of paper textures to be used. The NoisyOffice team did this.
\item Similarly, any markup features may be generated and overlaid by the same methods.
\item Documents can be digitized with a commercial scanner, or converted to a continuous analog signal and back with a fax machine.
\item The finished document image can be used as a texture and attached to a 3D mesh, then projected back to 2 dimensions to simulate physical deformation. DocCreator has a function to do this.
\end{enumerate}

@@

\section{Augraphy}
We were unable to find any tools for producing training images of modern documents, in a way suitable for automated use. The Augraphy library is our attempt at filling this gap.\\

@@

Augraphy attempts to decompose the lifetime of features accumulating in a document by separating the pipeline into three phases: ink, paper, and post. The ink phase exists to sequence effects which specifically alter the printed ink — like bleedthrough from too much ink on page, extraneous lines or regions from a mechanically faulty printer, or fading over time — and transform them prior to "printing". The paper phase is concerned with transformations of the underlying paper on which the ink gets printed; here we find the PaperFactory generator for creating a random texture from a set of given texture images, as well as effects like random noise, shadowing, watermarking, and staining. After the ink and paper textures are computed separately, they are merged in the manner of Technique 1 from the previous section, simulating the printing of the document. After "printing", the document enters the post-phase, wherein it may undergo alterations that would affect an already-printed document out in the world. Augmentations are available here which simulate the printed page being folded along multiple axes, marked by handwriting or highlighter, faxed, photocopied, scanned, photographed, burned, stained, and so on. Figure 1 shows the individual phases of an example pipeline combining to produce a noised document image.
\begin{figure}
\includegraphics[width=\textwidth]{pipeline.png}
\caption{Visualization of an Augraphy pipeline.} \label{fig1}
\end{figure}

\section{The Augraphy API}
The library was developed in Python, to allow maximal accessibility for practitioners, and was designed with an object-oriented structure, with concerns divided across a class hierarchy. When composed, different parts of the library interact to produce complex sequences of document image transformations, generating new synthetically-augmented datasets.\\

Modern frameworks for machine learning like \texttt{fastai} \cite{ref_fastai} aim to simplify the data handling requirements, and concordantly, the Augraphy development team takes great pains to ensure our library's ease-of-use and compatibility. We wanted the library to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so great care was taken to establish good defaults. The default Augraphy pipeline makes use of all of the augmentations available in Augraphy, with starting parameters selected after manual visual inspection of several thousand images. Adding a diverse array of realistic features to documents can be done with the following five-line incantation:
\begin{lstlisting}[language=Python]
from augraphy import *
pipeline = default_augraphy_pipeline()
img = cv2.imread("image.png")
data = pipeline.augment(img)
augmented_img = data["output"]
\end{lstlisting}

\subsection{Base}
\texttt{augraphy.base} is the core of the library, containing the central class for augmentations, another class for sequences of augmentations, and the pipeline class itself. The base classes exist to coordinate the compilation of discrete transformations into a larger pipeline, and to facilitate the operation and maintenance of these.\\

There are four ''main sequence'' classes in \texttt{augraphy.base}, which together provide the bulk of the library's functionality. Two additional classes, \texttt{OneOf} and \texttt{PaperFactory}, provide additional variation to pipelines in ways explored soon.

\subsubsection{Augmentation}
Augmentation is the most basic class in the project, and essentially exists as a thin wrapper over a probability value in the interval [0,1]. Every augmentation object is constructed with a probability of that augmentation being applied during the execution of a pipeline containing it.\\

@@

\subsubsection{AugmentationResult}
After an augmentation is applied, the output of its execution is stored in an \texttt{AugmentationResult} object and passed forward through the pipeline. These objects also record an exact copy of the augmentation object that was instantiated and applied, as well as any metadata that might be relevant for debugging or other advanced use.

\subsubsection{AugmentationSequence}
A list of \texttt{Augmentation}s -- together with the intent to apply those Augmentations in sequence -- determines an \texttt{AugmentationSequence}, which is itself both an \texttt{Augmentation} and callable. In practice, these are the model for the pipeline phases discussed previously; they are essentially lists of \texttt{Augmentation} constructor calls which produce callable \texttt{Augmentation} objects of the various flavors explored in . \texttt{AugmentationSequences} are applied to the image during each of the \texttt{AugmentationPipeline} phases, and in each case yield the image, transformed by some of the Augmentations in the sequence.

\subsubsection{AugmentationPipeline}
The bulk of the innovation in Augraphy resides in the Augmentation pipeline, which is an abstraction over one or more events in a physical document's life. Events in this case could be the initial printing of the document when ink adhered to the paper material, or several weeks later when the document was adhered to a public board, annotated, defaced, and torn away from its securing staples. Fifty years later, our protagonist page resurfaces in the library archive during routine preservation-scanning efforts. Conservationists use delicate tools to gently position and record an image of the document, storing this in a public repository. An \texttt{AugmentationPipeline} can model this entire sequence of events, or any individual event within.\\

@@

The value added by the \texttt{AugrapyPipeline} class over a bare list of functions mapped over an image is principally in the collection of metadata: the output of an \texttt{AugraphyPipeline} application is a Python dictionary which contains not only the final image, but copies of every intermediate image, as well as information about the object constructors and their parameters that were used for each augmentation. This allows for easy inspection and fine-tuning of the pipeline definition to achieve outputs with desired features.

\subsubsection{OneOf}
Real-world processes generally allow for objects to exist in multiple states over time. To model the possibility that a document image has undergone one and only one of a collection of augmentations, we use \texttt{OneOf}, which simply selects one of those augmentations from a given list, and uses this to modify the image.

\subsubsection{PaperFactory}
We often print on multiple sizes and kinds of paper, and out in the world we certainly \textit{encounter} such diverse documents. We introduce this variation into the \texttt{AugmentationPipeline} by including \texttt{PaperFactory} in the \texttt{paper} phase of the pipeline. This augmentation checks a local directory for images of paper to crop, scale, and use as a background for the document image. The pipeline contains edge detection logic for lifting only text and other foreground objects from a clean image, greatly simplifying the "printing" onto another "sheet", and capturing in a reproducible way the construction method used to generate the NoisyOffice database. Taken together, \texttt{PaperFactory} makes it effectively possible to re-print a document onto other surfaces, like hemp paper, cardboard, or wood.

\subsection{Augmentations}
The \texttt{base} modules provide scaffolding for working with general transformations on document images, called \texttt{augmentations}. We have already included many such transforms in the standard library, and have also provided utilities for easily building new augmentations and integrating them into the Augraphy workflow.\\

@@

Figures 2 and 3 contain representative images of each augmentation applied to this very document. Descriptions of and motivation for each augmentation are available on GitHub \footnote{\url{https://github.com/sparkfish/augraphy}}.

\begin{figure}
\includegraphics[width=\textwidth]{augmentations1.png}
\caption{Examples of each augmentation.} \label{fig2}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{augmentations2.png}
\caption{Examples of each augmentation.} \label{fig3}
\end{figure}

\subsection{Utilities}\label{utilities}
Interoperability and flexibility are core requirements of any data augmentation library, so Augraphy includes several utility classes designed to improve developer experience. Chief among these are \texttt{ComposePipelines}, \texttt{Foreign}, and \texttt{ImageOverlay}, which respectively

\begin{enumerate}
\item provide a means of composing two pipelines into one, allowing for the construction of complex pipeline algebras,
\item wrap augmentations from projects like \texttt{Albumentations} \cite{ref_albumentations} and \texttt{imgaug} \cite{ref_imgaug}, and
\item uses various blending algorithms to fuse foreground and background images together, useful for simulating "printing".
\end{enumerate}
\section{Deep Learning with Augraphy}
Augraphy aims to facilitate rapid dataset creation, advancing the state of the art for document image analysis tasks. This section describes a brief experiment using Augraphy to augment the NoisyOffice set, producing a corpus that is used to train a denoising convolutional neural network which outperforms an identically-structured model trained on only the provided NoisyOffice data. We continue to return to this database when testing our model training pipelines and new architectures, and felt it an appropriate jumping-off point for Augraphy analysis.

\subsection{Model Architecture}
To evaluate Augraphy, we trained a U-net convolutional neural network, built with the Keras library. This network achieved a high score on the NoisyOffice Kaggle competition \footnote{\url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}}; we selected this one for its simplicity and the clarity of its exposition, and use it with few changes.\\

This low-layer model contains two layers of a convolution, each followed by a rectified linear unit activation function, then a batch normalization layer as the encoding step. After the encoding step, max pooling is applied, followed by dropout, to improve translation invariance of feature encoding and to avoid overfitting respectively. The decoding step closely mirrors the encoding step, and contains two layers of ReLU-activated convolutions followed by a batch normalization layer, but with the convolution dimensions reversed; in this case the model is "unpacking" higher-dimensional features from its low-dimensional latent representation. After the decoding step, we perform 2-dimensional upsampling, compensating for the 2D max pooling applied earlier. Finally, the output of previous layers is convolved with a 3x3 kernel, while retaining the same image dimensions. This final convolution uses the sigmoid function as its activation function. All convolution steps use a 3x3 kernel and pad edges with zeroes, the max pooling and upsampling steps both use 2x2 kernels, and a 50\% unit dropout rate was used.

\subsection{Data Generation}
Despite recent techniques [Training Vision Transformers with Only 2040 Images, Vision Transformer for Small-Size Datasets, Training a Vision Transformer from scratch in less than 24 hours with 1 GPU] for reducing the volume of input data required to train models, data remains king; feeding a model more data during training can help ensure better latent representations of more features, improving robustness of the model and increasing its ability to generalize.\\

@@

\begin{lstlisting}
ink_phase = []
paper_phase = []
post_phase = [BadPhotoCopy(), Markup()]

AugraphyPipeline(ink_phase, paper_phase, post_phase)
\end{lstlisting}
\subsection{Training Regime}
We fit the model architecture described in the previous section to both the NoisyOffice corpus and a derivative work generated with Augraphy applied to the NoisyOffice ground truth images.\\

@@

Both models were trained with mean squared error as the loss function, using the Adam optimizer, and evaluated with the mean average error metric.

\begin{table}
\centering
\caption{Model training statistics}\label{tab1}
\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
\hline
Model & NoisyOffice & Augraphy\\
\hline
Average Loss & 0.0010 & 0.0014\\
Mean Average Error & 0.0150 & 0.0142\\
Validation Loss & 7.4609e-04 & 8.9985e-04\\
Validation Mean Average Error & 0.0122 & 0.0112\\
Training Time & 190ms/step & 218ms/step\\
\hline
\end{tabular}
\end{table}

\subsection{Results}
Sample predictions from each model on the validation task are presented in Figure 1. As expected, the NoisyOffice model performs admirably, but does struggle to fully remove the coffee stain feature, leaving some residue. The Augraphy model clearly outperforms the NoisyOffice model at stain removal, but does not generalize well to the folding and wrinkling noise; this was expected, since the Augraphy training data did not include fold or wrinkle features. Further, the Augraphy model overcompensates for the \texttt{BadPhotoCopy} behavior on text, by increasing the line thickness in the predicted text, resulting in a bold font.\\

\begin{figure}\label{fig4}
\includegraphics[width=\textwidth]{sidebyside.png}
\caption{Validation images (left), with the images predicted by the NoisyOffice (center) and Augraphy (right) models.} \label{fig4}
\end{figure}
